Covariate analysis of ROSMAP Reprocessed RNASeq

### 2016-09-02 code/Rmd/ROSMAP_RNASeq_Reprocessed_NonConditionedCogdx.Rmd

knit2synapse::knitToFolderEntity(file = "./ROSMAP_RNASeq_Reprocessed_NonConditionedCogdx.Rmd",
                                 parentId ="syn5570291",
                                 entityName = 'ROSMAP RNASeq Reprocessed Counts 2 (Based on cogdx)')
```

@@

# Code
CODE <- Folder(name = "ROSMAP RNASeq Reprocessed Counts 2 (Based on cogdx)", parentId = parentId)
CODE <- synStore(CODE)

>>>>

knit2synapse::knitToFolderEntity(file = "./ROSMAP_RNASeq_Reprocessed_NonConditionedCogdx.Rmd",
                                 parentId ="syn5570291",
                                 entityName = 'ROSMAP RNASeq Reprocessed Counts UnConditioned (Based on cogdx)')
```

@@

# Code
CODE <- Folder(name = "ROSMAP RNASeq Reprocessed Counts UnConditioned (Based on cogdx)", parentId = parentId)
CODE <- synStore(CODE)
